Data Management for LSST Special Programs

### 2023-11-09 ap_spcs.tex
WFD program --> Main Survey

The steps used to describe the hypothetical processing for each case scenario are: \\
Step 1. Data acquisition. \\
Step 2. Regular Prompt processing and Alert Production. \\
Step 3. Special Processing with reconfigured pipelines. \\
Step 4. Regular processing for inclusion in WFD program data products. \\
Step 5. User-Generated Processing. \\

@@

Step 2. Regular Prompt processing and Alert Production. \\
Each $2\times15$ second standard visit is processed by the Prompt pipeline 
and alerts are released within 60 seconds.
Within 24 hours, the {\tt DiaSource} and {\tt DiaObject} catalogs are updated
to include the results of Prompt processing of these visits.
After 80 hours, the processed visit images and difference images become available.
All images and sources originating from this Special Program have 
region and program labels, e.g., ``SP-OSSO".

@@

Step 4. Regular processing for inclusion in WFD program data products. \\
Every year, each $2\times15$ second standard visit is reprocessed by the DIA data release pipelines
and the results are included alongside WFD program data in the relevant DIA data products
(e.g., processed visit images, difference images, associated source catalogs).
In the first year after the Special Program is executed,
Rubin Data Management finds that 10\% of the standard visits from this Special Program
had coordinates and image quality that help improve uniformity of the all-sky coadd,
and so they are included.
In later years, this fraction decreases (remember, this is \emph{hypothetical}).
In all data releases, any and all processed images and catalog sources that originate in visits from this Special Program
have the same region and program labels, e.g., ``SP-OSSO".

@@

Step 2. Regular Prompt processing and Alert Production. \\
Same as above, but the program label would be, e.g., ``SP-DDF-COSMOS".

Step 3. Special Processing with reconfigured pipelines. \\
First, a template image of appropriate depth for ``nightly" difference imaging is created.
At the end of each nightly sequence of observations, a pipeline based on recongfigured 
components of the LSST Science Pipelines is automatically triggered.
This pipeline creates nightly coadds in each filter and runs DIA using the template.
Alerts are \emph{not} produced, but unique and separate catalogs with the same format
as {\tt DiaObject} and {\tt DiaSource} are updated within 24 hours (not a requirement).
At the end of each season, deeply coadded images that include all of the DDF's visits 
from all years are re-generated, along with a separate {\tt Object}-like catalog.
All images and catalogs are stored in separate butler collections and TAP tables from
the WFD program data products.

Step 4. Regular processing for inclusion in WFD program data products. \\
Every year, each standard visit is reprocessed by the DIA data release pipelines
and the results are included alongside WFD program data in the relevant DIA data products
(e.g., processed visit images, difference images, associated source catalogs).
Due to their small dither and lack of rotation, not even a single DDF image 
is used to supplement the WFD program's all-sky coadd.

@@

Step 4. Regular processing for inclusion in WFD program data products. \\
These short-exposure, high sky background images would not contribute to the data products created for the WFD program.

>>>>

The steps used to describe the hypothetical processing for each case scenario are: \\
Step 1. Data acquisition. \\
Step 2. Regular Prompt processing and Alert Production. \\
Step 3. Special Processing with reconfigured pipelines. \\
Step 4. Regular processing for inclusion in Main Survey data products. \\
Step 5. User-Generated Processing. \\

@@

Step 2. Regular Prompt processing and Alert Production. \\
Each $2\times15$ second standard visit is processed by the Prompt pipeline 
and alerts are released within 60 seconds.
Within 24 hours, the {\tt DiaSource} and {\tt DiaObject} catalogs are updated
to include the results of Prompt processing of these visits.
After 80 hours, the processed visit images and difference images become available.
All images and sources originating from this Special Program have 
region and observing mode labels, e.g., ``SP-OSSO".

@@

Step 4. Regular processing for inclusion in Main Survey data products. \\
Every year, each $2\times15$ second standard visit is reprocessed by the DIA data release pipelines
and the results are included alongside Main Survey data in the relevant DIA data products
(e.g., processed visit images, difference images, associated source catalogs).
In the first year after the Special Program is executed,
Rubin Data Management finds that 10\% of the standard visits from this Special Program
had coordinates and image quality that help improve uniformity of the all-sky coadd,
and so they are included.
In later years, this fraction decreases (remember, this is \emph{hypothetical}).
In all data releases, any and all processed images and catalog sources that originate in visits from this Special Program
have the same region and observing mode labels, e.g., ``SP-OSSO".

@@

Step 2. Regular Prompt processing and Alert Production. \\
Same as above, but the observing mode label might be, e.g., ``SP-DDF-COSMOS".

Step 3. Special Processing with reconfigured pipelines. \\
First, a template image of appropriate depth for ``nightly" difference imaging is created.
At the end of each nightly sequence of observations, a pipeline based on recongfigured 
components of the LSST Science Pipelines is automatically triggered.
This pipeline creates nightly coadds in each filter and runs DIA using the template.
Alerts are \emph{not} produced, but unique and separate catalogs with the same format
as {\tt DiaObject} and {\tt DiaSource} are updated within 24 hours (not a requirement).
At the end of each season, deeply coadded images that include all of the DDF's visits 
from all years are re-generated, along with a separate {\tt Object}-like catalog.
All images and catalogs are stored in separate butler collections and TAP tables from
the Main Survey data products.

Step 4. Regular processing for inclusion in Main Survey data products. \\
Every year, each standard visit is reprocessed by the DIA data release pipelines
and the results are included alongside Main Survey data in the relevant DIA data products
(e.g., processed visit images, difference images, associated source catalogs).
Due to their small dither and lack of rotation, not even a single DDF image 
is used to supplement the Main Survey's all-sky coadd.

@@

Step 4. Regular processing for inclusion in Main Survey data products. \\
These short-exposure, high sky background images would not contribute to the data products created for the Main Survey.
